# Developing Data Products Course Project
### Author: Dominik Vuksan

For the final project in the Developing Data Products Course, we'll be making  a shiny application and it's documentation (both presentation in R Markdown and R Markdown document). So, let's start.

```{r}
library(shiny)
```

First, we will make the UI. In general, I like to start with the server first (which I did, but I am showing the UI first because the UI was first when I was learning making shiny applications) because I'm always defining my variables, and then writing the code for the UI.

```{r}
ui= fluidPage(
  titlePanel("Predicting the stopping distance with speed for 1920's cars."),
  #shows us the most upper text, which is considered to be the title
  sidebarLayout( # telling R we are doing the sidebar
    sidebarPanel( # telling R how is the sidebar going to look
      h3("Slide me!"), # the text telling to slide the slider
      sliderInput("sliderSpeed","Speed(mph)", 0, 60, value = 15) # this is the slider!
    ),
    mainPanel(
      plotOutput("plot"), # the plot 
      h3("Stopping distance prediction based on speed."),
      textOutput("pred") # the predicted value
  )
)) # so, this was the user interface layout
```

Then we move on with the server code which show us what is happening in the background while we are sliding and waiting for the results.

```{r}
server= function(input, output){
  
  data= datasets::cars # reading the data in
  model= lm(dist~speed, data) # linear model
  pred= reactive({
    speedInput= input$sliderSpeed
    predict(model, newdata= data.frame(speed= speedInput))
  }) # prediction
  output$plot= renderPlot({
    speedInput= input$sliderSpeed
    plot(data$speed, data$dist,
         xlab= "MPH", ylab="Distance (ft)",
         bty= "n", xlim= c(0,200), ylim= c(0,200))
    abline(model, col= "blue", lwd= 1)
    points(speedInput, pred(), col= "red", pch=19) # the graph with the red dot prediction
  })
  output$predDist= renderText({
    pred()
  })
}
```

After both UI and server being coded, we run the app and that's it.

```{r}
shinyApp(ui= ui, server= server)
```
